A Bayesian approach to burial networks to infer social changes in northeastern Taiwan during the European colonization period

### 2021-01-06 analysis/paper/paper.Rmd
change figure names

image_width_1_col_inch = 90/25.4 # image Single column	w = 90 mm 
image_width_2_col_inch = 190/25.4 # image Double column w = 190 mm 
image_width_3_col_inch = 190/19
```

@@

```{r burial-map, fig.cap = "Map illustrating the location of burials by periods at the central excavation area of Kiwulan (each square is 4 X 4 meters). The gray dots are post holes.", fig.width = image_width_2_col_inch}
KWL_burial_map
```

@@

```{r ergm-terms-table}
ergm_terms <- readxl::read_excel(here::here("analysis", "data", "raw_data", "ergm_term.xlsx")) 
knitr::kable(ergm_terms,
             caption = "The parameters of exponential random graph models for a undirected network to corresponding with archaeological evidence.")
```

@@

```{r make-network-diagrams, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("005-network-diagrams-two-phases.R"))}
suppressWarnings(source(here::here("analysis", "paper", "005-network-diagrams-two-phases.R")))
```

@@

```{r network-diagrams, fig.cap = "A: Burial network before the European arrival, B: Burial network after the European arrival. The size of the nodes is proportional to the node degrees that means the number of connections to a node. The thickness of tie represents the number of goods in common between nodes.", fig.width = image_width_3_col_inch}
diagrams_two_phases
```

>>>>

image_width_1_col_inch = 90/25.4 # image Single column	w = 90 mm 
image_width_2_col_inch = 190/25.4 # image Double column w = 190 mm 
image_width_3_col_inch = 190/19

```

@@

```{r figure-burial-map, fig.cap = "Map illustrating the location of burials by periods at the central excavation area of Kiwulan (each square is 4 X 4 meters). The gray dots are post holes."}
knitr::include_graphics(here::here("analysis", "figures", "002-burial-map.png"))
```

@@

```{r table-ergm-terms}
ergm_terms <- readxl::read_excel(here::here("analysis", "data", "raw_data", "ergm_term.xlsx")) 
knitr::kable(ergm_terms,
             caption = "The parameters of exponential random graph models for a undirected network to corresponding with archaeological evidence.")
```

@@

@@

```{r network-diagrams, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("005-network-diagrams-two-phases.R"))}
suppressWarnings(source(here::here("analysis", "paper", "005-network-diagrams-two-phases.R")))
```

```{r figure-network-diagrams, fig.cap = "Map illustrating the location of burials by periods at the central excavation area of Kiwulan (each square is 4 X 4 meters). The gray dots are post holes."}
knitr::include_graphics(here::here("analysis", "figures", "005-network-diagrams.png"))
```
